---
title: "R Notebook"
output: html_notebook
---

1.  Set working directory

```{r}
setwd("~/Library/CloudStorage/OneDrive-UniversityofEdinburgh/4th year/dissertation/dissertation")
```

2.  Load packages

```{r, message=FALSE}
library(skimr)  #summary
library(tidyverse)
library(lubridate)  #dates management
library(gridExtra)  #arrange plots
```

3.  Load the data and see its structure

```{r}
data <- read.csv("Data_PAM_Scott_Base.csv") # load data
skimr::skim(data)  # see a summary of the whole data
str(data)  # see the structure of each variable
tail(data)  # view the last 6 rows of data
head(data)  # view the first 6 rows of data
```

Data of sensors 1,2 and 4 are for the moss and 3 is for the lichen. Data is from Jan 2019 to Feb 2022. I am going to consider summer form 1 Nov to 15 Feb. I currently have data for 3 summers: 2019-2020, 2020-2021, 2021-2022.

## 4. Format data in a way that is going to be useful to me

4.1. Remove weird times and dates and divide the useful ones

```{r}
data_clean <- data[, -c(2:13)]  # create a new data set without columns 2 to 13

data_clean <- data_clean %>% 
  mutate(Date = parse_date_time(Datetime, 'dmy HM'))   # indicate the format the date is wanted

print(data_clean[is.na(data_clean$Date), ])  # Check for rows with parsing issues

#  Row 584 is problematic

data_clean[584, 1]<-"10/02/2019 10:08"  # Change the value to the correct one 

data_clean <- data_clean %>% 
  mutate(Date = parse_date_time(Datetime, 'dmy HM'))   # repeat with all the lines working

data_clean <- data_clean %>%  # create new columns with month, year,
  mutate(Month = month(Date), # day, minute                     
         Year = year(Date),
         Day = day(Date),
         Hour = hour(Date),
         Minute = minute(Date))

data_clean[584,]  # check it worked
```

4.2. Check the new data

```{r, echo= TRUE, results='hide'}
str(data_clean)
skimr::skim(data_clean)
```

4.3. Change the diff columns names to match the rest of columns

```{r}

data_clean<-data_clean %>% 
  rename(X1.diff = diff,
         X2.diff = diff.1,
         X3.diff = diff.2,
         X4.diff = diff.3)
```

4.4. Need to change some variables of format

```{r, warning = FALSE}

data_clean <- data_clean %>%
  mutate(X1.PAR = as.numeric(X1.PAR),  # Change PAR of X1, X2 and X3 to numeric
         X2.PAR = as.numeric(X2.PAR), 
         X3.PAR = as.numeric(X3.PAR), 
         X4.PAR = as.numeric(X4.PAR),
         X3.F = as.numeric(X3.F),  # Change F and Fm to numeric
         X3.Fm. = as.numeric(X3.Fm.),
         X3.Temp = as.numeric(X3.Temp),  # Change Temp 3 to numeric
         X1.diff = as.numeric(X1.diff),  # Change all diff to numeric
         X2.diff = as.numeric(X2.diff),
         X3.diff = as.numeric(X3.diff),
         X4.diff = as.numeric(X4.diff),
         Month = as.factor(Month),  # Change day, month and year to categories
         Year = as.factor(Year), 
         Day = as.factor(Day))
```

4.5. Create column for month (in letters) and day-month

```{r}
data_clean <- data_clean %>% 
  mutate(Month_Name = as.factor(case_when(  # Make a column with the names of the months and make them a factor
  Month == 1 ~ "Jan",  # case_when from dplyr package
  Month == 2 ~ "Feb",
  Month == 3 ~ "Mar",
  Month == 4 ~ "Apr",
  Month == 5 ~ "May",
  Month == 6 ~ "Jun",
  Month == 7 ~ "Jul",
  Month == 8 ~ "Aug",
  Month == 9 ~ "Sep",
  Month == 10 ~ "Oct",
  Month == 11 ~ "Nov",
  Month == 12 ~ "Dec"))) %>% 
  mutate(Date_Combined = as.factor(  # Make a column with the day and month name separated by -
    paste(Month_Name, Day, sep = "-")))  # Make the column a factor
```

4.6. Create a column for average moss values of yield,PAR, F, Fm, Temp, ETR and diff

```{r}
data_clean <- data_clean %>% 
  mutate(av_moss_yield = rowMeans(data_clean[, c("X1.Y..II.", "X2.Y..II.", "X4.Y..II.")]),  # rowMeans gets the mean of each row in the data frame and stores the result in a new column
         av_moss_PAR = rowMeans(data_clean[, c("X1.PAR", "X2.PAR", "X4.PAR")]),
         av_moss_F = rowMeans(data_clean[, c("X1.F", "X2.F", "X4.F")]),
         av_moss_Fm = rowMeans(data_clean[, c("X1.Fm.", "X2.Fm.", "X4.Fm.")]),
         av_moss_temp = rowMeans(data_clean[, c("X1.Temp", "X2.Temp", "X4.Temp")]),
         av_moss_ETR = rowMeans(data_clean[, c("X1.ETR", "X2.ETR", "X4.ETR")]),
         av_moss_diff = rowMeans(data_clean[, c("X1.diff", "X2.diff", "X4.diff")]))
```

## 5. Subset data for summers 2019-2020, 2020-2021, 2021-2022

**Summer 2019-2020**

This includes the data from the 1-Nov 2019 to the 15 of Feb 2020

```{r}
summer_19_20 <- data_clean %>% 
  filter(Year == 2019 & Month %in% c(11,12) |  # Filter all data points in Nov, Dec 2019 and Jan, Feb 2020
           Year == 2020 & Month %in% c(1,2)) %>% 
  filter(!(Month == 2 & Day > 15))  # remove days over the 15th of Feb

# Check our data

head(summer_19_20)  # First 6 rows 
tail(summer_19_20)  # Last 6 rows
```

**Summer 2020-2021**

This includes the data from the 1-Nov 2020 to the 15 of Feb 2021

```{r}
summer_20_21 <- data_clean %>% 
  filter(Year == 2020 & Month %in% c(11,12) |  # Filter all data points in Nov, Dec 2029 and Jan, Feb 2021
           Year == 2021 & Month %in% c(1,2)) %>% 
  filter(!(Month == 2 & Day > 15))  # remove days over the 15th of Feb

# Check our data

head(summer_20_21)  # First 6 rows 
tail(summer_20_21)  # Last 6 rows
```

**Summer 2021-2022**

This includes the data from the 1-Nov 2021 to the 15 of Feb 2022.

\* I only have the data until the 3rd of Feb yet

```{r}
summer_21_22 <- data_clean %>% 
  filter(Year == 2021 & Month %in% c(11,12) |  # Filter all data points in Nov, Dec 2021 and Jan, Feb 2022
           Year == 2022 & Month %in% c(1,2)) %>% 
  filter(!(Month == 2 & Day > 15))  # remove days over the 15th of Feb

# Check our data

head(summer_21_22)  # First 6 rows 
tail(summer_21_22)  # Last 6 rows
```
