---
title: "figures_appendix"
author: "Ainhoa"
date: "2024-04-13"
output: html_document
---

Code to properly format the figures in the appendix. 

**WARNING: FIRST. RUN  Code_calc_yield.Rmd OTHERWISE IT WON'T. WORK**

- Function for graph asthetics

```{r, echo= TRUE, results="hide"}
theme_graphs_env_cond <- function(){
  theme_classic() +
  theme(axis.text.x = element_text(face = "bold",size = 10, angle = 90))+
   theme(axis.text = element_text(face = "bold", size = 10),  # Adjust the size as needed
          axis.title = element_text(face = "bold", size = 12),
        legend.text = element_text(face = "bold", size= 12)) 
  
  }
```



# APPENDIX 1. CLOSEUP ON ACTIVITY AND MICROCLIMATE IN MARCH 2022

```{r}

(temp_plot_march_22_23 <- data_clean %>% 
   filter(Day_cum > 44620 & Day_cum < 44652) %>% # Filter days from 28th Feb 2022 until 1st April 2022
   mutate(Date_Combined = reorder(Date_Combined, Day_cum)) %>%  # reorder the factors of Date_Combined according to the values of Day_cum. Do it for each subset individually because factors repeat for each year
   ggplot() +
   geom_line(aes(Date, X1.Temp, color = "Bryum argemteum X1"))+  # Add a line that joins the points
   geom_line(aes(Date, X2.Temp, color = "Bryum argemteum X2"))+  # Add a line that joins the points
   geom_line(aes(Date, X3.Temp, color = "Austroplaca soropelta"))+  # Add a line that joins the points
   geom_line(aes(Date, X4.Temp, color = "Bryum argemteum X4"))+  # Add a line that joins the points
   geom_hline(yintercept = 0, color = "blue", linetype = "dashed") +
      scale_color_manual(values = c( "Austroplaca soropelta" = "#ff914d", 
                                  "Bryum argemteum X1" = "#119683", 
                                  "Bryum argemteum X2" = "#74c476", 
                                  "Bryum argemteum X4" = "#41ab5d")) +
   labs(x = "\nDate (day)", y = "TT (°C)") +
   theme_graphs_env_cond() +
    theme(axis.text.x = element_blank(), 
           axis.ticks.x = element_blank(),
           axis.title = element_text(face = "bold", size = 12),
           axis.text.y = element_text(face = "bold", size = 10),
           axis.title.x = element_blank(),
          legend.position = "none"))  # Remove axis label and text for the graph)


(PAR_plot_march_22_23 <- data_clean %>% 
   filter(Day_cum > 44620 & Day_cum < 44652) %>% # Filter days from 28th Feb 2022 until 1st April 2022
   mutate(Date_Combined = reorder(Date_Combined, Day_cum)) %>%  # reorder the factors of Date_Combined 
    # according to the values of Day_cum. Do it for each subset individually because factors repeat for each year
  ggplot() +
   geom_line(aes(Date, X1.PAR, color = "Bryum argemteum X1"))+  # Add a line that joins the points
   geom_line(aes(Date, X2.PAR, color = "Bryum argemteum X2"))+  # Add a line that joins the points
   geom_line(aes(Date, X3.PAR, color = "Austroplaca soropelta"))+  # Add a line that joins the points
   geom_line(aes(Date, X4.PAR, color = "Bryum argemteum X4"))+  # Add a line that joins the points
  scale_color_manual(values = c( "Austroplaca soropelta" = "#ff914d", 
                                  "Bryum argemteum X1" = "#119683", 
                                  "Bryum argemteum X2" = "#74c476", 
                                  "Bryum argemteum X4" = "#41ab5d")) +
  labs(color = "Species") + # This adds a legend for the colors
   labs(x = "\nDate 2023 (day)", y = "PAR \n(µmol \nm-2 s^-1)") +
  ylim(c(0, 1500))+
   scale_y_continuous(breaks = seq(0, 500, by = 200)) +  # Remove axis label and text for the graph
   theme_graphs_env_cond()+
        theme(axis.text.x = element_text(angle = 45, hjust = 1, face = "bold", size = 10),
           axis.title = element_text(face = "bold", size = 12),
           axis.text.y = element_text(face = "bold", size = 10),
           legend.position = "bottom",
           legend.title = element_text(face = "bold", size = 12),
           legend.text = element_text(face = "bold", size= 10))+
         guides(color = guide_legend(ncol = 2)))  # Split legend into two columns


(Yield_plot_march_22_23 <- data_clean %>% 
   filter(Day_cum > 44620 & Day_cum < 44652)%>% # Filter days from 28th Feb 2022 until 1st April 2022
   mutate(Date = reorder(Date_Combined, Day_cum)) %>%  # reorder the factors of Date_Combined according to the values of Day_cum. Do it for each subset individually because factors repeat for each year
   ggplot() +
   geom_point(aes(Datetime, X1.Y, color = "Bryum argemteum X1"))+  # Add a line that joins the points
   geom_point(aes(Datetime, X2.Y, color = "Bryum argemteum X2"))+  # Add a line that joins the points
   geom_point(aes(Datetime, X3.Y, color = "Austroplaca soropelta"))+  # Add a line that joins the points
   geom_point(aes(Datetime, X4.chosen_yield, color = "Bryum argemteum X4"))+  # Add a line that joins the points
   geom_line(aes(Datetime, X1.Y, color = "Bryum argemteum X1"))+  # Add a line that joins the points
   geom_line(aes(Datetime, X2.Y, color = "Bryum argemteum X2"))+  # Add a line that joins the points
   geom_line(aes(Datetime, X3.Y, color = "Austroplaca soropelta"))+  # Add a line that joins the points
   geom_line(aes(Datetime, X4.chosen_yield, color = "Bryum argemteum X4"))+  # Add a line that joins the points
      scale_color_manual(values = c( "Austroplaca soropelta" = "#ff914d", 
                                  "Bryum argemteum X1" = "#119683", 
                                  "Bryum argemteum X2" = "#74c476", 
                                  "Bryum argemteum X4" = "#41ab5d")) +
  scale_y_continuous(breaks = seq(0, 0.5, by = 0.2), limits = c(0, 0.5)) +
   labs(x = "\nDate (day)", y = "Yield") +
   theme_graphs_env_cond() +
    theme(axis.text.x = element_blank(), 
           axis.ticks.x = element_blank(),
           axis.title = element_text(face = "bold", size = 12),
           axis.text.y = element_text(face = "bold", size = 10),
           axis.title.x = element_blank(),
          legend.position = "none"))  # Remove axis label and text for the graph)


(ETR_plot_march_22_23 <- data_clean %>% 
   filter(Day_cum > 44620 & Day_cum < 44652) %>% # Filter days from 28th Feb 2022 until 1st April 2022
   mutate(Date_Combined = reorder(Date_Combined, Day_cum)) %>%  # reorder the factors of Date_Combined according to the values of Day_cum. Do it for each subset individually because factors repeat for each year
   ggplot() +
   geom_line(aes(Date, X1.ETR, color = "Bryum argemteum X1"))+  # Add a line that joins the points
   geom_line(aes(Date, X2.ETR, color = "Bryum argemteum X2"))+  # Add a line that joins the points
   geom_line(aes(Date, X3.ETR, color = "Austroplaca soropelta"))+  # Add a line that joins the points
   geom_line(aes(Date, X4.chosen_ETR, color = "Bryum argemteum X4"))+  # Add a line that joins the points
   scale_color_manual(values = c( "Austroplaca soropelta" = "#ff914d", 
                                  "Bryum argemteum X1" = "#119683", 
                                  "Bryum argemteum X2" = "#74c476", 
                                  "Bryum argemteum X4" = "#41ab5d")) +
   scale_y_continuous(breaks = seq(0, 0.5, by = 0.2), limits = c(0, 0.5)) +
   labs(x = "\nDate (day)", y = "ETR\n(μmol e- \nm−2s−1)") +
   theme_graphs_env_cond() +
    theme(axis.text.x = element_blank(), 
           axis.ticks.x = element_blank(),
           axis.title = element_text(face = "bold", size = 12),
           axis.text.y = element_text(face = "bold", size = 10),
           axis.title.x = element_blank(),
          legend.position = "none",    
          legend.text = element_text(size = 12, face = "bold"),  # Adjust the font size of legend text
          legend.title = element_text(size = 12, face = "bold")))  # Adjust the font size of legend title)
  
  
(Ft_plot_march_22_23 <- data_clean %>% 
   filter(Day_cum > 44620 & Day_cum < 44652) %>% # Filter days from 28th Feb 2022 until 1st April 2022
   mutate(Date_Combined = reorder(Date_Combined, Day_cum)) %>%  # reorder the factors of Date_Combined according to the values of Day_cum. Do it for each subset individually because factors repeat for each year
   ggplot() +
   geom_line(aes(Date, X1.F, color = "Bryum argemteum X1"))+  # Add a line that joins the points
   geom_line(aes(Date, X2.F, color = "Bryum argemteum X2"))+  # Add a line that joins the points
   geom_line(aes(Date, X3.F, color = "Austroplaca soropelta"))+  # Add a line that joins the points
   geom_line(aes(Date, X4.F, color = "Bryum argemteum X4"))+  # Add a line that joins the points
      scale_color_manual(values = c( "Austroplaca soropelta" = "#ff914d", 
                                  "Bryum argemteum X1" = "#119683", 
                                  "Bryum argemteum X2" = "#74c476", 
                                  "Bryum argemteum X4" = "#41ab5d")) +
   labs(x = "\nDate (day)", y = "Ft") +
   theme_graphs_env_cond() +
    theme(axis.text.x = element_blank(), 
           axis.ticks.x = element_blank(),
           axis.title = element_text(face = "bold", size = 12),
           axis.text.y = element_text(face = "bold", size = 10),
           axis.title.x = element_blank(),
          legend.position = "none")+  # Remove axis label and text for the graph)
    scale_y_continuous(breaks = seq(0, 100, by = 15)))  # Remove axis label and text for the graph


(Fm_plot_march_22_23 <- data_clean %>% 
   filter(Day_cum > 44620 & Day_cum < 44652) %>% # Filter days from 28th Feb 2022 until 1st April 2022
   mutate(Date_Combined = reorder(Date_Combined, Day_cum)) %>%   # reorder the factors of Date_Combined according to the values of Day_cum. 
    # Do it for each subset individually because factors repeat for each year
   ggplot() +
   geom_line(aes(Date, X1.Fm, color = "Bryum argemteum X1"))+  # Add a line that joins the points
   geom_line(aes(Date, X2.Fm, color = "Bryum argemteum X2"))+  # Add a line that joins the points
   geom_line(aes(Date, X3.Fm, color = "Austroplaca soropelta"))+  # Add a line that joins the points
   geom_line(aes(Date, X4.Fm, color = "Bryum argemteum X4"))+  # Add a line that joins the points
      scale_color_manual(values = c( "Austroplaca soropelta" = "#ff914d", 
                                  "Bryum argemteum X1" = "#119683", 
                                  "Bryum argemteum X2" = "#74c476", 
                                  "Bryum argemteum X4" = "#41ab5d")) +
   labs(x = "\nDate (day)", y = "Fm") +
   theme_graphs_env_cond() +
    theme(axis.text.x = element_blank(), 
           axis.ticks.x = element_blank(),
           axis.title = element_text(face = "bold", size = 12),
           axis.text.y = element_text(face = "bold", size = 10),
           axis.title.x = element_blank(),
          legend.position = "none")+  # Remove axis label and text for the graph)
    scale_y_continuous(breaks = seq(0, 100, by = 15)))  # Remove axis label and text for the graph


(Diff_plot_march_22_23 <- data_clean %>% 
   filter(Day_cum > 44620 & Day_cum < 44652) %>% # Filter days from 28th Feb 2022 until 1st April 2022
   mutate(Date_Combined = reorder(Date_Combined, Day_cum)) %>%  # reorder the factors of Date_Combined according to the values of Day_cum. Do it for each subset individually because factors repeat for each year
   ggplot() +
   geom_line(aes(Date, X1.diff, color = "Bryum argemteum X1"))+  # Add a line that joins the points
   geom_line(aes(Date, X2.diff, color = "Bryum argemteum X2"))+  # Add a line that joins the points
   geom_line(aes(Date, X3.diff, color = "Austroplaca soropelta"))+  # Add a line that joins the points
   geom_line(aes(Date, X4.diff, color = "Bryum argemteum X4"))+  # Add a line that joins the points
      scale_color_manual(values = c( "Austroplaca soropelta" = "#ff914d", 
                                  "Bryum argemteum X1" = "#119683", 
                                  "Bryum argemteum X2" = "#74c476", 
                                  "Bryum argemteum X4" = "#41ab5d")) +
  geom_hline(yintercept = 5, color = "blue", linetype = "dashed") +
   labs(x = "\nDate (day)", y = "Fm-Ft ") +  # a.u. means arbitrary unit
  ylim(c(-1.5, 8))+
   theme_graphs_env_cond() +
    theme(axis.text.x = element_blank(), 
           axis.ticks.x = element_blank(),
           axis.title = element_text(face = "bold", size = 12),
           axis.text.y = element_text(face = "bold", size = 10),
           axis.title.x = element_blank(),
          legend.position = "none")+  # Remove axis label and text for the graph)
    scale_y_continuous(breaks = seq(-1.5, 8, by = 3)))



(combined_plot_march_22_23 <- (ETR_plot_march_22_23/Ft_plot_march_22_23/Fm_plot_march_22_23/Diff_plot_march_22_23/Yield_plot_march_22_23/temp_plot_march_22_23/PAR_plot_march_22_23) & plot_layout(ncol = 1))

ggsave(filename = "graphs_year_round/march_october/combined_plot_march_22_23.png", combined_plot_march_22_23, width = 16,height = 18, units = "cm", device = "png")  # Save graph
```

# APPENDIX 4. graphs to characterise under snow

## 1. Create functions for theme and labs across plots

Temperature
```{r}
theme_temp <- function() {
  theme(
    axis.text.x = element_blank(),
    axis.title.x = element_blank(),
    axis.ticks.x = element_blank()
  )
}

# need to apply it after the graph

labs_temp <- function(plot) {
  plot + 
  labs(x = "\nDate (day)", y = "TT (ºC)\nLichen") +
  scale_y_continuous(breaks = seq(-20, 10, by = 10), limits = c(-20, 10))
}

```

PAR

```{r}
theme_PAR <- function() {
    theme(axis.text.x = element_text(face = "bold", size = 10))
}


# need to apply it after the graph

labs_PAR <- function(plot) {
   plot +
   labs(y = "PAR\n(µmol \nm-2 s^-1)") +
   scale_x_datetime(date_breaks = "3 day", 
                    date_labels = "%d - %b",
                    date_minor_breaks = "1 day") +
   scale_y_continuous(breaks = seq(0, 2000, by = 400), 
                     limits = c(0, 2000))
}
```

Yield

```{r}
theme_yield <- function() {
theme(axis.text.x = element_blank(),
        axis.title.x = element_blank(),
        axis.ticks.x = element_blank())  # Remove axis label and text for the graph)
}

# need to apply it after the graph

labs_yield <- function(plot) { 
  plot +
    scale_y_continuous(breaks = seq(0, 0.8, by = 0.2), limits = c(0, 0.8))
}
```

ETR

```{r}
theme_ETR <- function() {
    theme(axis.text.x = element_blank(),
        axis.title.x = element_blank(),
        axis.ticks.x = element_blank())  # Remove axis label and text for the graph)
}

# need to apply it after the graph

labs_ETR <- function(plot) { 
  plot +
   labs(x = "\nDate (day)", y = "ETR\n(μmol e- \nm−2s−1)") +
  scale_y_continuous(breaks = seq(0, 500, by = 150), limits = c(0, 500))
}
```

Fm
```{r}

theme_fm <- function() {
    theme(axis.text.x = element_blank(),
        axis.title.x = element_blank(),
        axis.ticks.x = element_blank())  # Remove axis label and text for the graph)
}

# need to apply it after the graph

labs_fm <- function(plot) {
  plot +
    scale_y_continuous(breaks = seq(0, 1000, by = 200), limits = c(0, 1000))
}
```

## 2. Graphs Lichen
1. Summer 2019-2020

Sample X3 (Lichen)

```{r}
(temp_plot_19_20_X3 <- summer_19_20 %>% 
   ggplot(aes(Date, X3.Temp)) +
   geom_line()+  # add a line that joins the points
   geom_hline(yintercept = 0, color = "blue", linetype = "dashed") +
   labs(x = "\nDate (day)", y = "TT \n(ºC) ") +
   theme_graphs_env_cond()+
   xlim(as.POSIXct(c("2019-11-01 00:08:00", "2020-02-29 23:53:00"), tz = "UTC"))+
   theme(axis.text.x = element_blank(),
        axis.title.x = element_blank(),
        axis.ticks.x = element_blank()))

(PAR_plot_19_20_X3 <-summer_19_20 %>% 
    ggplot(aes(Date, X3.PAR)) +
   geom_line()+  # add a line that joins the points
   labs(x = "\nDate 2019-2020 (day)") +
   labs(y = "PAR\n(µmol \nm-2 s^-1)") +
  scale_y_continuous(breaks = seq(0, 2000, by = 400), limits = c(0, 2000))+
   scale_x_datetime(date_breaks = "3 day", 
                    date_labels = "%d - %b",
                    date_minor_breaks = "1 day") +
   theme_graphs_env_cond() +
    theme(axis.text.x = element_text(face = "bold", size = 10)))


(Yield_plot_19_20_X3 <- summer_19_20 %>% 
   ggplot(aes(Date, X3.Y)) +
   geom_line()+  # Add a line that joins the points
   labs(x = "\nDate (day)", y = "Yield \nLichen ") +
   theme_graphs_env_cond() +
    xlim(as.POSIXct(c("2019-11-01 00:08:00", "2020-02-29 23:53:00"), tz = "UTC"))+
    scale_y_continuous(breaks = seq(0, 0.8, by = 0.2), limits = c(0, 0.8))+
    theme(axis.text.x = element_blank(),
        axis.title.x = element_blank(),
        axis.ticks.x = element_blank()))  # Remove axis label and text for the graph)

(ETR_plot_19_20_X3 <- summer_19_20 %>% 
   ggplot(aes(Date, X3.ETR)) +
   geom_line()+  # Add a line that joins the points
   labs(x = "\nDate (day)", y = "ETR\n(μmol e- \nm−2s−1) \nLichen") +
  scale_y_continuous(breaks = seq(0, 500, by = 150), limits = c(0, 500))+
   theme_graphs_env_cond() +
    xlim(as.POSIXct(c("2019-11-01 00:08:00", "2020-02-29 23:53:00"), tz = "UTC"))+
    theme(axis.text.x = element_blank(),
        axis.title.x = element_blank(),
        axis.ticks.x = element_blank()))  # Remove axis label and text for the graph)

(Fm_plot_19_20_X3 <- summer_19_20 %>% 
   ggplot(aes(Date, X3.Fm)) +
   geom_line()+  # Add a line that joins the points
   labs(x = "\nDate (day)", y = "Fm \nLichen") +
   theme_graphs_env_cond() +
    xlim(as.POSIXct(c("2019-11-01 00:08:00", "2020-02-29 23:53:00"), tz = "UTC"))+
    theme(axis.text.x = element_blank(),
        axis.title.x = element_blank(),
        axis.ticks.x = element_blank())+  # Remove axis label and text for the graph
    scale_y_continuous(breaks = seq(0, 1000, by = 200), limits = c(0, 1000)))  

(combined_plot_19_20_X3 <- (ETR_plot_19_20_X3/Fm_plot_19_20_X3/Yield_plot_19_20_X3/temp_plot_19_20_X3/PAR_plot_19_20_X3) & plot_layout(ncol = 1)) 

ggsave(filename = "graphs_appendix/austroplaca/combined_plot_19_20_X3.png", combined_plot_19_20_X3, width = 18,height = 12, units = "cm", device = "png")  # Save graph


```

2. Summer 2020-2021

Sample X3 (Lichen) **Changed yield!!**

```{r}
temp_plot_20_21_X3 <- summer_20_21 %>% 
   ggplot(aes(Date, X3.Temp)) +
   geom_line()+  # Add a line that joins the points
   geom_hline(yintercept = 0, color = "blue", linetype = "dashed") +
   labs(x = "\nDate (day)", y = "Temperature (ºC)\nLichen X3") +
   theme_graphs_env_cond() +
   theme_temp()

(temp_plot_20_21_X3 <- labs_temp(temp_plot_20_21_X3)) 


PAR_plot_20_21_X3 <-summer_20_21 %>% 
    ggplot(aes(Date, X3.PAR)) +
   geom_line()+  # add a line that joins the points
   labs(x = "\nDate 2020-2021(day)", y = "PAR \n(µmol m-2 s^-1)") +
   theme_graphs_env_cond()+
  theme_PAR()

(PAR_plot_20_21_X3 <- labs_PAR(PAR_plot_20_21_X3))

Yield_plot_20_21_X3 <- summer_20_21 %>% 
   ggplot(aes(Date, X3.chosen_yield)) +
   geom_line()+  # Add a line that joins the points
   labs(x = "\nDate (day)", y = "Yield \nLichen X3 ") +
   theme_graphs_env_cond() +
    theme(axis.text.x = element_blank(),
        axis.title.x = element_blank())+  # Remove axis label and text for the graph)
   theme_yield()

(Yield_plot_20_21_X3 <- labs_yield(Yield_plot_20_21_X3))
    
    
    
ETR_plot_20_21_X3 <- summer_20_21 %>% 
   ggplot(aes(Date, X3.chosen_ETR)) +
   geom_line()+  # Add a line that joins the points
   labs(x = "\nDate (day)", y = "ETR\n(μmol e- m−2s−1) \nLichen X3 ") +
   theme_graphs_env_cond() +
    theme(axis.text.x = element_blank(),
        axis.title.x = element_blank()) +  # Remove axis label and text for the graph)
theme_ETR()

(ETR_plot_20_21_X3 <- labs_ETR(ETR_plot_20_21_X3))
    
    
Fm_plot_20_21_X3 <- summer_20_21 %>% 
   ggplot(aes(Date, X3.Fm)) +
   geom_line()+  # Add a line that joins the points
   labs(x = "\nDate (day)", y = "Fm \nLichen X3 ") +
   theme_graphs_env_cond() +
    theme(axis.text.x = element_blank(),) +
    scale_y_continuous(breaks = seq(0, 500, by = 50))+
  theme_fm() 

(Fm_plot_20_21_X3 <- labs_fm(Fm_plot_20_21_X3))


(combined_plot_20_21_X3 <- (ETR_plot_20_21_X3/Fm_plot_20_21_X3/Yield_plot_20_21_X3/temp_plot_20_21_X3/PAR_plot_20_21_X3) & plot_layout(ncol = 1))

ggsave(filename = "graphs_appendix/austroplaca/combined_plot_20_21_X3.png", combined_plot_20_21_X3, width = 18,height = 12, units = "cm", device = "png")  # Save graph

```

3. Summer 2021-2022

Sample X3 (lichen)

```{r}
(temp_plot_21_22_X3 <- summer_21_22 %>% 
   ggplot(aes(Date, X3.Temp)) +
   geom_line()+  # Add a line that joins the points
   geom_hline(yintercept = 0, color = "blue", linetype = "dashed") +
   labs(x = "\nDate (day)", y = "TT (°C)") +
   theme_graphs_env_cond() +
    theme(axis.text.x = element_blank(),
        axis.title.x = element_blank()) +  # Remove axis label and text for the graph
theme_temp())

(temp_plot_21_22_X3 <- labs_temp(temp_plot_21_22_X3))

(PAR_plot_21_22_X3 <-summer_21_22 %>% 
    ggplot(aes(Date, X3.PAR)) +
   geom_line()+  # add a line that joins the points
   labs(x = "\nDate 2021-2022 (day)", y = "PAR \n(µmol m-2 s^-1)") +
   theme_graphs_env_cond()+
   theme_PAR())

(PAR_plot_21_22_X3 <-labs_PAR(PAR_plot_21_22_X3))

(Yield_plot_21_22_X3 <- summer_21_22 %>% 
   ggplot(aes(Date, X3.Y)) +
   geom_line()+  # Add a line that joins the points
   labs(x = "\nDate (day)", y = "Yield \n Lichen") +
   theme_graphs_env_cond() +
    theme(axis.text.x = element_blank(),
        axis.title.x = element_blank()) + # Remove axis label and text for the graph
theme_yield())

(Yield_plot_21_22_X3 <- labs_yield(Yield_plot_21_22_X3))


(ETR_plot_21_22_X3 <- summer_21_22 %>% 
   ggplot(aes(Date, X3.ETR)) +
   geom_line()+  # Add a line that joins the points
   labs(x = "\nDate (day)", y = "ETR\n(μmol e- m−2s−1) \nLichen") +
   theme_graphs_env_cond() +
    theme(axis.text.x = element_blank(),
        axis.title.x = element_blank()) +  # Remove axis label and text for the graph)
theme_ETR())

(ETR_plot_21_22_X3 <- labs_ETR(ETR_plot_21_22_X3))

(Fm_plot_21_22_X3 <- summer_21_22 %>% 
   ggplot(aes(Date, X3.Fm)) +
   geom_line()+  # Add a line that joins the points
   labs(x = "\nDate (day)", y = "Fm \nLichen ") +
   theme_graphs_env_cond() +
    theme(axis.text.x = element_blank(),
        axis.title.x = element_blank())+  # Remove axis label and text for the graph
    scale_y_continuous(breaks = seq(0, 1000, by = 50))+
    theme_fm())

(Fm_plot_21_22_X3 <- labs_fm(Fm_plot_21_22_X3))

(combined_plot_21_22_X3 <- (ETR_plot_21_22_X3/Fm_plot_21_22_X3/Yield_plot_21_22_X3/temp_plot_21_22_X3/PAR_plot_21_22_X3) & plot_layout(ncol = 1))

ggsave(filename = "graphs_appendix/austroplaca/combined_plot_21_22_X3.png", combined_plot_21_22_X3, width = 18,height = 12, units = "cm", device = "png")  # Save graph

```

4. Summer 2022-2023

Sample X3 (Lichen) **Changed yield!!**

```{r}
(temp_plot_22_23_X3 <- summer_22_23 %>% 
   ggplot(aes(Date, X3.Temp)) +
   geom_line()+  # Add a line that joins the points
   geom_hline(yintercept = 0, color = "blue", linetype = "dashed") +
   labs(x = "\nDate (day)", y = "Temperature \nMoss X3 (°C)") +
   theme_graphs_env_cond() +
    theme(axis.text.x = element_blank(),
        axis.title.x = element_blank())+  # Remove axis label and text for the graph
   theme_temp())

(temp_plot_22_23_X3 <- labs_temp(temp_plot_22_23_X3))

(PAR_plot_22_23_X3 <-summer_22_23 %>% 
    ggplot(aes(Date, X3.PAR)) +
   geom_line()+  # add a line that joins the points
   labs(x = "\nDate 2022-2023 (day)", y = "PAR \n(µmol m-2 s^-1)") +
   theme_graphs_env_cond() +
  theme_PAR())

(PAR_plot_22_23_X3 <- labs_PAR(PAR_plot_22_23_X3))

(Fm_plot_22_23_X3 <- summer_22_23 %>% 
   ggplot(aes(Date, X3.Fm)) +
   geom_line()+  # Add a line that joins the points
   labs(x = "\nDate (day)", y = "Fm \nLichen X3 ") +
   theme_graphs_env_cond() +
    theme(axis.text.x = element_blank(),
        axis.title.x = element_blank()) +  # Remove axis label and text for the graph 
    scale_y_continuous(breaks = seq(0, 500, by = 50))+
    theme_fm())

(Fm_plot_22_23_X3 <- labs_fm(Fm_plot_22_23_X3))

(Yield_plot_22_23_X3 <- summer_22_23 %>% 
   ggplot(aes(Date, X3.chosen_yield)) +
   geom_line()+  # Add a line that joins the points
   labs(x = "\nDate (day)", y = "Yield \n Lichen X3 ") +
   theme_graphs_env_cond() +
    theme(axis.text.x = element_blank(),
        axis.title.x = element_blank()) +  # Remove axis label and text for the graph
theme_yield())

(Yield_plot_22_23_X3 <- labs_yield(Yield_plot_22_23_X3))

(ETR_plot_22_23_X3 <- summer_22_23 %>% 
  ggplot(aes(Date, X3.chosen_ETR))+
  geom_line()+  # Add a line that joins the points
  labs(x = "\nDate (day)", y = "ETR\n(μmol e- m−2s−1) \n Lichen X3 ") +  
  theme_graphs_env_cond() +
  theme(axis.text.x = element_blank(),
        axis.title.x = element_blank())) # Remove axis label and text for the graph

(ETR_plot_22_23_X3 <- labs_ETR(ETR_plot_22_23_X3))

(combined_plot_22_23_X3 <- (ETR_plot_22_23_X3/Fm_plot_22_23_X3/Yield_plot_22_23_X3/temp_plot_22_23_X3/PAR_plot_22_23_X3) & plot_layout(ncol = 1))

ggsave(filename = "graphs_appendix/austroplaca/combined_plot_22_23_X3.png", combined_plot_22_23_X3, width = 18 ,height = 12, units = "cm", device = "png")  # Save graph
```

### Make plot for Bryum Argeteum (Sample X1, X2, X4)

1. Summer 2019-2020

Sample X1 (moss)

```{r}

(temp_plot_19_20_X1 <- summer_19_20 %>% 
   ggplot(aes(Date, X1.Temp)) +
   geom_line()+  # Add a line that joins the points
   geom_hline(yintercept = 0, color = "blue", linetype = "dashed") +
   labs(x = "\nDate (day)", y = "Temperature \nMoss X1 (°C)") +
   theme_graphs_env_cond() +
    theme(axis.text.x = element_blank(),
        axis.title.x = element_blank()) +  # Remove axis label and text for the graph
   theme_temp())
 
 (temp_plot_19_20_X1 <- labs_temp(temp_plot_19_20_X1))

(PAR_plot_19_20_X1 <-summer_19_20 %>% 
    ggplot(aes(Date, X1.PAR)) +
   geom_line()+  # add a line that joins the points
   labs(x = "\nDate 2019-2020 (day)", y = "PAR \n(µmol m-2 s^-1)") +
   theme_graphs_env_cond() +
  theme_PAR())

(PAR_plot_19_20_X1 <- labs_PAR(PAR_plot_19_20_X1))

(Yield_plot_19_20_X1 <- summer_19_20 %>% 
   ggplot(aes(Date, X1.Y)) +
   geom_line()+  # Add a line that joins the points
   labs(x = "\nDate (day)", y = "Yield \nMoss X1 ") +
   theme_graphs_env_cond() +
    theme(axis.text.x = element_blank(),
        axis.title.x = element_blank())+  # Remove axis label and text for the graph)
    theme_yield())

(Yield_plot_19_20_X1 <- labs_yield(Yield_plot_19_20_X1))

(ETR_plot_19_20_X1 <- summer_19_20 %>% 
   ggplot(aes(Date, X1.ETR)) +
   geom_line()+  # Add a line that joins the points
   labs(x = "\nDate (day)", y = "ETR\n(μmol e- m−2s−1) \nMoss X1 ") +
   theme_graphs_env_cond() +
    theme(axis.text.x = element_blank(),
        axis.title.x = element_blank()) +  # Remove axis label and text for the graph)
   theme_ETR())
    
(ETR_plot_19_20_X1 <- labs_ETR(ETR_plot_19_20_X1))    
    
(Fm_plot_19_20_X1 <- summer_19_20 %>% 
   ggplot(aes(Date, X1.Fm)) +
   geom_line()+  # Add a line that joins the points
   labs(x = "\nDate (day)", y = "Fm \nMoss X1 ") +
   theme_graphs_env_cond() +
    theme(axis.text.x = element_blank(),
        axis.title.x = element_blank())+  # Remove axis label and text for the graph
    scale_y_continuous(breaks = seq(0, 1000, by = 50))+
    theme_fm())

(Fm_plot_19_20_X1 <- labs_fm(Fm_plot_19_20_X1))


(combined_plot_19_20_X1 <- (ETR_plot_19_20_X1/Fm_plot_19_20_X1/Yield_plot_19_20_X1/temp_plot_19_20_X1/PAR_plot_19_20_X1) & plot_layout(ncol = 1))

ggsave(filename = "graphs_appendix/bryum/combined_plot_19_20_X1.png", combined_plot_19_20_X1, width = 18,height = 12, units = "cm", device = "png")  # Save graph
```

Sample X2 (moss)

```{r}
(temp_plot_19_20_X2 <- summer_19_20 %>% 
   ggplot(aes(Date, X2.Temp)) +
   geom_line()+  # add a line that joins the points
   geom_hline(yintercept = 0, color = "blue", linetype = "dashed") +
   labs(x = "\nDate (day)", y = "Temperature (°C)\nMoss X2") +
   theme_graphs_env_cond()+
   theme(axis.text.x = element_blank(),
        axis.title.x = element_blank())+
   theme_temp())

(temp_plot_19_20_X2 <- labs_temp(temp_plot_19_20_X2))

(PAR_plot_19_20_X2 <-summer_19_20 %>% 
    ggplot(aes(Date, X2.PAR)) +
   geom_line()+  # add a line that joins the points
   labs(x = "\nDate 2019-2020 (day)", y = "PAR \n(µmol m-2 s^-1)") +
   theme_graphs_env_cond()+
  theme_PAR())

(PAR_plot_19_20_X2 <- labs_PAR(PAR_plot_19_20_X2))
  
(Yield_plot_19_20_X2 <- summer_19_20 %>% 
   ggplot(aes(Date, X2.Y)) +
   geom_line()+  # Add a line that joins the points
   labs(x = "\nDate (day)", y = "Yield \nMoss X2 ") +
   theme_graphs_env_cond() +
   theme(axis.text.x = element_blank(),
        axis.title.x = element_blank())+  # Remove axis label and text for the graph)
   theme_yield())

(Yield_plot_19_20_X2 <- labs_yield(Yield_plot_19_20_X2))

(ETR_plot_19_20_X2 <- summer_19_20 %>% 
   ggplot(aes(Date, X2.ETR)) +
   geom_line()+  # Add a line that joins the points
   labs(x = "\nDate (day)", y = "ETR\n(μmol e- m−2s−1) \nMoss X2 ") +
   theme_graphs_env_cond() +
   theme(axis.text.x = element_blank(),
        axis.title.x = element_blank()) +  # Remove axis label and text for the graph)
   theme_ETR())

(ETR_plot_19_20_X2 <- labs_ETR(ETR_plot_19_20_X2))

(Fm_plot_19_20_X2 <- summer_19_20 %>% 
   ggplot(aes(Date, X2.Fm)) +
   geom_line()+  # Add a line that joins the points
   labs(x = "\nDate (day)", y = "Fm \nMoss X2 ") +
   theme_graphs_env_cond() +
    theme(axis.text.x = element_blank(),
        axis.title.x = element_blank())+  # Remove axis label and text for the graph
    scale_y_continuous(breaks = seq(0, 1000, by = 50))+
    theme_fm())

(Fm_plot_19_20_X2 <- labs_fm(Fm_plot_19_20_X2))

(combined_plot_19_20_X2 <- (ETR_plot_19_20_X2/Fm_plot_19_20_X2/Yield_plot_19_20_X2/temp_plot_19_20_X2/PAR_plot_19_20_X2) & plot_layout(ncol = 1))

ggsave(filename = "graphs_appendix/bryum/combined_plot_19_20_X2.png", combined_plot_19_20_X2, width = 18,height = 12, units = "cm", device = "png")  # Save graph
```

Sample X4 (Moss)

```{r}
(temp_plot_19_20_X4 <- summer_19_20 %>% 
   ggplot(aes(Date, X4.Temp)) +
   geom_line()+  # add a line that joins the points
   geom_hline(yintercept = 0, color = "blue", linetype = "dashed") +
   labs(x = "\nDate (day)", y = "Temperature \nMoss X4 (°C)") +
   theme_graphs_env_cond()+
   theme(axis.text.x = element_blank(),
        axis.title.x = element_blank())+
   theme_temp())

(temp_plot_19_20_X4 <- labs_temp(temp_plot_19_20_X4))

(PAR_plot_19_20_X4 <-summer_19_20 %>% 
    ggplot(aes(Date, X4.PAR)) +
   geom_line()+  # add a line that joins the points
   labs(x = "\nDate 2019-2020 (day)", y = "PAR \n(µmol m-2 s^-1)") +
   theme_graphs_env_cond()+
   theme_PAR())

(PAR_plot_19_20_X4 <- labs_PAR(PAR_plot_19_20_X4))

(Yield_plot_19_20_X4 <- summer_19_20 %>% 
   ggplot(aes(Date, X4.Y)) +
   geom_line()+  # Add a line that joins the points
   labs(x = "\nDate (day)", y = "Yield \nMoss X4 ") +
   theme_graphs_env_cond() +
    theme(axis.text.x = element_blank(),
        axis.title.x = element_blank())+  # Remove axis label and text for the graph)
  theme_yield())

(Yield_plot_19_20_X4 <- labs_yield(Yield_plot_19_20_X4))

(ETR_plot_19_20_X4 <- summer_19_20 %>% 
   ggplot(aes(Date, X4.ETR)) +
   geom_line()+  # Add a line that joins the points
   labs(x = "\nDate (day)", y = "ETR\n(μmol e- m−2s−1) \nMoss X4 ") +
   theme_graphs_env_cond() +
   theme(axis.text.x = element_blank(),
        axis.title.x = element_blank()) +  # Remove axis label and text for the graph
   theme_ETR())

(ETR_plot_19_20_X4 <- labs_ETR(ETR_plot_19_20_X4))

(Fm_plot_19_20_X4 <- summer_19_20 %>% 
   ggplot(aes(Date, X4.Fm)) +
   geom_line()+  # Add a line that joins the points
   labs(x = "\nDate (day)", y = "Fm \nMoss X4 ") +
   theme_graphs_env_cond() +
    theme(axis.text.x = element_blank(),
        axis.title.x = element_blank()) +  # Remove axis label and text for the graph
    scale_y_continuous(breaks = seq(0, 1700, by = 50))+ 
    theme_fm())

(Fm_plot_19_20_X4 <- labs_fm(Fm_plot_19_20_X4))


(combined_plot_19_20_X4 <- (ETR_plot_19_20_X4/Fm_plot_19_20_X4/Yield_plot_19_20_X4/temp_plot_19_20_X4/PAR_plot_19_20_X4) & plot_layout(ncol = 1)) 

ggsave(filename = "graphs_appendix/bryum/combined_plot_19_20_X4.png", combined_plot_19_20_X4, width = 18,height = 12, units = "cm", device = "png")  # Save graph

```

2. Summer 2020-2021

Sample X1 (Moss)

```{r}
(temp_plot_20_21_X1 <- summer_20_21 %>% 
   ggplot(aes(Date, X1.Temp)) +
   geom_line()+  # Add a line that joins the points
   geom_hline(yintercept = 0, color = "blue", linetype = "dashed") +
   labs(x = "\nDate (day)", y = "Temperature \nMoss X1 (°C)") +
   theme_graphs_env_cond() +
    theme(axis.text.x = element_blank(),
        axis.title.x = element_blank())+  # Remove axis label and text for the graph
   theme_temp())

(temp_plot_20_21_X1<- labs_temp(temp_plot_20_21_X1))

(PAR_plot_20_21_X1 <- summer_20_21 %>% 
    ggplot(aes(Date, X1.PAR)) +
   geom_line()+  # add a line that joins the points
   labs(x = "\nDate 2020-2021 (day)", y = "PAR \n(µmol m-2 s^-1)") +
   theme_graphs_env_cond()+
  theme_PAR())

(PAR_plot_20_21_X1 <- labs_PAR(PAR_plot_20_21_X1))

(Yield_plot_20_21_X1 <- summer_20_21 %>% 
   ggplot(aes(Date, X1.Y)) +
   geom_line()+  # Add a line that joins the points
   labs(x = "\nDate (day)", y = "Yield \nMoss X1 ") +
   theme_graphs_env_cond() +
    theme(axis.text.x = element_blank(),
        axis.title.x = element_blank())+  # Remove axis label and text for the graph)
    theme_yield())

(Yield_plot_20_21_X1 <- labs_yield(Yield_plot_20_21_X1))

(ETR_plot_20_21_X1 <- summer_20_21 %>% 
   ggplot(aes(Date, X1.ETR)) +
   geom_line()+  # Add a line that joins the points
   labs(x = "\nDate (day)", y = "ETR\n(μmol e- m−2s−1) \nMoss X1 ") +
   theme_graphs_env_cond() +
   theme(axis.text.x = element_blank(),
        axis.title.x = element_blank()) +  # Remove axis label and text for the graph)
   theme_ETR())

(ETR_plot_20_21_X1 <- labs_ETR(ETR_plot_20_21_X1))

(Fm_plot_20_21_X1 <- summer_20_21 %>% 
   ggplot(aes(Date, X1.Fm)) +
   geom_line()+  # Add a line that joins the points
   labs(x = "\nDate (day)", y = "Fm \nMoss X1 ") +
   theme_graphs_env_cond() +
    theme(axis.text.x = element_blank(),
        axis.title.x = element_blank())+  # Remove axis label and text for the graph
    scale_y_continuous(breaks = seq(0, 1000, by = 50))+
    theme_fm())

(Fm_plot_20_21_X1 <- labs_fm(Fm_plot_20_21_X1))

(combined_plot_20_21_X1 <- (ETR_plot_20_21_X1/Fm_plot_20_21_X1/Yield_plot_20_21_X1/temp_plot_20_21_X1/PAR_plot_20_21_X1) & plot_layout(ncol = 1))

ggsave(filename = "graphs_appendix/bryum/combined_plot_20_21_X1.png", combined_plot_20_21_X1, width = 16,height = 12, units = "cm", device = "png")  # Save graph
```

Sample X2 (Moss)

```{r}
(temp_plot_20_21_X2 <- summer_20_21 %>% 
   ggplot(aes(Date, X2.Temp)) +
   geom_point()+  # Add points for the data
   geom_line()+  # Add a line that joins the points
   geom_hline(yintercept = 0, color = "blue", linetype = "dashed") +
   labs(x = "\nDate (day)", y = "Temperature \nMoss X2 (°C)") +
   theme_graphs_env_cond() +
    theme(axis.text.x = element_blank(),
        axis.title.x = element_blank())+  # Remove axis label and text for the graph
   theme_temp())

(temp_plot_20_21_X2<- labs_temp(temp_plot_20_21_X2))

(PAR_plot_20_21_X2 <- summer_20_21 %>% 
    ggplot(aes(Date, X2.PAR)) +
   geom_line()+  # add a line that joins the points
   labs(x = "\nDate 2020-2021 (day)", y = "PAR \n(µmol m-2 s^-1)") +
   theme_graphs_env_cond()+
  theme_PAR())

(PAR_plot_20_21_X2 <- labs_PAR(PAR_plot_20_21_X2))

(Yield_plot_20_21_X2 <- summer_20_21 %>% 
   ggplot(aes(Date, X2.Y)) +
   geom_line()+  # Add a line that joins the points
   labs(x = "\nDate (day)", y = "Yield \nMoss X2 ") +
   theme_graphs_env_cond() +
    theme(axis.text.x = element_blank(),
        axis.title.x = element_blank())+  # Remove axis label and text for the graph)
    theme_yield())

(Yield_plot_20_21_X2 <- labs_yield(Yield_plot_20_21_X2))

(ETR_plot_20_21_X2 <- summer_20_21 %>% 
   ggplot(aes(Date, X2.ETR)) +
   geom_line()+  # Add a line that joins the points
   labs(x = "\nDate (day)", y = "ETR\n(μmol e- m−2s−1) \nMoss X2 ") +
   theme_graphs_env_cond() +
   theme(axis.text.x = element_blank(),
        axis.title.x = element_blank()) +  # Remove axis label and text for the graph)
   theme_ETR())

(ETR_plot_20_21_X2 <- labs_ETR(ETR_plot_20_21_X2))

(Fm_plot_20_21_X2 <- summer_20_21 %>% 
   ggplot(aes(Date, X2.Fm)) +
   geom_line()+  # Add a line that joins the points
   labs(x = "\nDate (day)", y = "Fm \nMoss X2 ") +
   theme_graphs_env_cond() +
    theme(axis.text.x = element_blank(),
        axis.title.x = element_blank())+  # Remove axis label and text for the graph
    scale_y_continuous(breaks = seq(0, 1000, by = 50))+
    theme_fm())

(Fm_plot_20_21_X2 <- labs_fm(Fm_plot_20_21_X2))

(combined_plot_20_21_X2 <- (ETR_plot_20_21_X2/Fm_plot_20_21_X2/Yield_plot_20_21_X2/temp_plot_20_21_X2/PAR_plot_20_21_X2) & plot_layout(ncol = 1))

ggsave(filename = "graphs_appendix/bryum/combined_plot_20_21_X2.png", combined_plot_20_21_X2, width = 16,height = 12, units = "cm", device = "png")  # Save graph
```

Sample X4 (moss)

```{r}
(temp_plot_20_21_X4 <- summer_20_21 %>% 
   ggplot(aes(Date, X4.Temp)) +
   geom_line()+  # Add a line that joins the points
   geom_hline(yintercept = 0, color = "blue", linetype = "dashed") +
   labs(x = "\nDate (day)", y = "Temperature \nMoss X4 (°C)") +
   theme_graphs_env_cond() +
    theme(axis.text.x = element_blank(),
        axis.title.x = element_blank())+  # Remove axis label and text for the graph
   theme_temp())

(temp_plot_20_21_X4<- labs_temp(temp_plot_20_21_X4))

(PAR_plot_20_21_X4 <- summer_20_21 %>% 
    ggplot(aes(Date, X4.PAR)) +
   geom_line()+  # add a line that joins the points
   labs(x = "\nDate 2020-2021 (day)", y = "PAR \n(µmol m-2 s^-1)") +
   theme_graphs_env_cond()+
  theme_PAR())

(PAR_plot_20_21_X4 <- labs_PAR(PAR_plot_20_21_X4))

(Yield_plot_20_21_X4 <- summer_20_21 %>% 
   ggplot(aes(Date, X4.Y)) +
   geom_line()+  # Add a line that joins the points
   labs(x = "\nDate (day)", y = "Yield \nMoss X4 ") +
   theme_graphs_env_cond() +
    theme(axis.text.x = element_blank(),
        axis.title.x = element_blank())+  # Remove axis label and text for the graph)
    theme_yield())

(Yield_plot_20_21_X4 <- labs_yield(Yield_plot_20_21_X4))

(ETR_plot_20_21_X4 <- summer_20_21 %>% 
   ggplot(aes(Date, X4.ETR)) +
   geom_line()+  # Add a line that joins the points
   labs(x = "\nDate (day)", y = "ETR\n(μmol e- m−2s−1) \nMoss X4 ") +
   theme_graphs_env_cond() +
   theme(axis.text.x = element_blank(),
        axis.title.x = element_blank()) +  # Remove axis label and text for the graph)
   theme_ETR())

(ETR_plot_20_21_X4 <- labs_ETR(ETR_plot_20_21_X4))

(Fm_plot_20_21_X4 <- summer_20_21 %>% 
   ggplot(aes(Date, X4.Fm)) +
   geom_line()+  # Add a line that joins the points
   labs(x = "\nDate (day)", y = "Fm \nMoss X4 ") +
   theme_graphs_env_cond() +
    theme(axis.text.x = element_blank(),
        axis.title.x = element_blank())+  # Remove axis label and text for the graph
    scale_y_continuous(breaks = seq(0, 1000, by = 50))+
    theme_fm())

(Fm_plot_20_21_X4 <- labs_fm(Fm_plot_20_21_X4))

(combined_plot_20_21_X4 <- (ETR_plot_20_21_X4/Fm_plot_20_21_X4/Yield_plot_20_21_X4/temp_plot_20_21_X4/PAR_plot_20_21_X4) & plot_layout(ncol = 1))

ggsave(filename = "graphs_appendix/bryum/combined_plot_20_21_X4.png", combined_plot_20_21_X4, width = 16,height = 12, units = "cm", device = "png")  # Save graph
```


3. Summer 2021-2022

Sample X1 (moss)

```{r}
(temp_plot_21_22_X1 <- summer_21_22 %>% 
   ggplot(aes(Date, X1.Temp)) +
   geom_line()+  # Add a line that joins the points
   geom_hline(yintercept = 0, color = "blue", linetype = "dashed") +
   labs(x = "\nDate (day)", y = "Temperature \nMoss X1 (°C)") +
   theme_graphs_env_cond() +
    theme(axis.text.x = element_blank(),
        axis.title.x = element_blank())+  # Remove axis label and text for the graph
   theme_temp())

(temp_plot_21_22_X1 <- labs_temp(temp_plot_21_22_X1))

(PAR_plot_21_22_X1 <-summer_21_22 %>% 
    ggplot(aes(Date, X1.PAR)) +
   geom_line()+  # add a line that joins the points
   labs(x = "\nDate 2021-2022 (day)", y = "PAR \n(µmol m-2 s^-1)") +
   theme_graphs_env_cond()+
  theme_PAR())

(PAR_plot_21_22_X1 <- labs_PAR(PAR_plot_21_22_X1))

(Yield_plot_21_22_X1 <- summer_21_22 %>% 
   ggplot(aes(Date, X1.Y)) +
   geom_line()+  # Add a line that joins the points
   labs(x = "\nDate (day)", y = "Yield \nMoss X1 ") +
   theme_graphs_env_cond() +
   theme(axis.text.x = element_blank(),
        axis.title.x = element_blank()) +  # Remove axis label and text for the graph
   theme_yield())

(Yield_plot_21_22_X1 <- labs_yield(Yield_plot_21_22_X1))

(ETR_plot_21_22_X1 <- summer_21_22 %>% 
   ggplot(aes(Date, X1.ETR)) +
   geom_line()+  # Add a line that joins the points
   labs(x = "\nDate (day)", y = "ETR\n(μmol e- m−2s−1) \nMoss X1") +
   theme_graphs_env_cond() +
   theme(axis.text.x = element_blank(),
        axis.title.x = element_blank()) +  # Remove axis label and text for the graph)
   theme_ETR())

(ETR_plot_21_22_X1 <- labs_ETR(ETR_plot_21_22_X1))

(Fm_plot_21_22_X1 <- summer_21_22 %>% 
   ggplot(aes(Date, X1.Fm)) +
   geom_line()+  # Add a line that joins the points
   labs(x = "\nDate (day)", y = "Fm \nMoss X1") +
   theme_graphs_env_cond() +
    theme(axis.text.x = element_blank(),
        axis.title.x = element_blank()) +# Remove axis label and text for the graph
    scale_y_continuous(breaks = seq(0, 1000, by = 50))) 

(Fm_plot_21_22_X1 <- labs_fm(Fm_plot_21_22_X1))

(combined_plot_21_22_X1 <- (ETR_plot_21_22_X1/Fm_plot_21_22_X1/Yield_plot_21_22_X1/temp_plot_21_22_X1/PAR_plot_21_22_X1) & plot_layout(ncol = 1))

ggsave(filename = "graphs_appendix/bryum/combined_plot_21_22_X1.png", combined_plot_21_22_X1, width = 16,height = 12, units = "cm", device = "png")  # Save graph

```

Sample X2 (moss)

```{r}
(temp_plot_21_22_X2 <- summer_21_22 %>% 
   ggplot(aes(Date, X2.Temp)) +
   geom_line()+  # Add a line that joins the points
   geom_hline(yintercept = 0, color = "blue", linetype = "dashed") +
   labs(x = "\nDate (day)", y = "Temperature \nMoss X2 (°C)") +
   theme_graphs_env_cond() +
    theme(axis.text.x = element_blank(),
        axis.title.x = element_blank())+  # Remove axis label and text for the graph
   theme_temp())

(temp_plot_21_22_X2 <- labs_temp(temp_plot_21_22_X2))

(PAR_plot_21_22_X2 <-summer_21_22 %>% 
    ggplot(aes(Date, X2.PAR)) +
   geom_line()+  # add a line that joins the points
   labs(x = "\nDate 2021-2022 (day)", y = "PAR \n(µmol m-2 s^-1)") +
   theme_graphs_env_cond()+
  theme_PAR())

(PAR_plot_21_22_X2 <- labs_PAR(PAR_plot_21_22_X2))

(Yield_plot_21_22_X2 <- summer_21_22 %>% 
   ggplot(aes(Date, X2.Y)) +
   geom_line()+  # Add a line that joins the points
   labs(x = "\nDate (day)", y = "Yield \nMoss X2 ") +
   theme_graphs_env_cond() +
   theme(axis.text.x = element_blank(),
        axis.title.x = element_blank()) +  # Remove axis label and text for the graph
   theme_yield())

(Yield_plot_21_22_X2 <- labs_yield(Yield_plot_21_22_X2))

(ETR_plot_21_22_X2 <- summer_21_22 %>% 
   ggplot(aes(Date, X2.ETR)) +
   geom_line()+  # Add a line that joins the points
   labs(x = "\nDate (day)", y = "ETR\n(μmol e- m−2s−1) \nMoss X2") +
   theme_graphs_env_cond() +
   theme(axis.text.x = element_blank(),
        axis.title.x = element_blank()) +  # Remove axis label and text for the graph)
   theme_ETR())

(ETR_plot_21_22_X2 <- labs_ETR(ETR_plot_21_22_X2))

(Fm_plot_21_22_X2 <- summer_21_22 %>% 
   ggplot(aes(Date, X2.Fm)) +
   geom_line()+  # Add a line that joins the points
   labs(x = "\nDate (day)", y = "Fm \nMoss X2") +
   theme_graphs_env_cond() +
    theme(axis.text.x = element_blank(),
        axis.title.x = element_blank()) +# Remove axis label and text for the graph
    scale_y_continuous(breaks = seq(0, 1000, by = 50))) 

(Fm_plot_21_22_X2 <- labs_fm(Fm_plot_21_22_X2))

(combined_plot_21_22_X2 <- (ETR_plot_21_22_X2/Fm_plot_21_22_X2/Yield_plot_21_22_X2/temp_plot_21_22_X2/PAR_plot_21_22_X2) & plot_layout(ncol = 1))

ggsave(filename = "graphs_appendix/bryum/combined_plot_21_22_X2.png", combined_plot_21_22_X2, width = 16,height = 12, units = "cm", device = "png")  # Save graph

```


Sample X4 (moss)

```{r}
(temp_plot_21_22_X4 <- summer_21_22 %>% 
   ggplot(aes(Date, X4.Temp)) +
   geom_line()+  # Add a line that joins the points
   geom_hline(yintercept = 0, color = "blue", linetype = "dashed") +
   labs(x = "\nDate (day)", y = "Temperature \nMoss X4 (°C)") +
   theme_graphs_env_cond() +
    theme(axis.text.x = element_blank(),
        axis.title.x = element_blank())+  # Remove axis label and text for the graph
   theme_temp())

(temp_plot_21_22_X4 <- labs_temp(temp_plot_21_22_X4))

(PAR_plot_21_22_X4 <-summer_21_22 %>% 
    ggplot(aes(Date, X4.PAR)) +
   geom_line()+  # add a line that joins the points
   labs(x = "\nDate 2021-2022 (day)", y = "PAR \n(µmol m-2 s^-1)") +
   theme_graphs_env_cond()+
  theme_PAR())

(PAR_plot_21_22_X4 <- labs_PAR(PAR_plot_21_22_X4))

(Yield_plot_21_22_X4 <- summer_21_22 %>% 
   ggplot(aes(Date, X4.chosen_yield)) +
   geom_line()+  # Add a line that joins the points
   labs(x = "\nDate (day)", y = "Yield \n Moss X4 ") +
   theme_graphs_env_cond() +
    theme(axis.text.x = element_blank(),
        axis.title.x = element_blank())+  # Remove axis label and text for the graph
    theme_yield())

(Yield_plot_21_22_X4 <- labs_yield(Yield_plot_21_22_X4))

(ETR_plot_21_22_X4 <- summer_21_22 %>% 
   ggplot(aes(Date, X4.chosen_ETR)) +
   geom_line()+  # Add a line that joins the points
   labs(x = "\nDate (day)", y = "ETR\n(μmol e- m−2s−1) \nMoss X4") +
   theme_graphs_env_cond() +
    theme(axis.text.x = element_blank(),
        axis.title.x = element_blank())+  # Remove axis label and text for the graph)
theme_ETR())

(ETR_plot_21_22_X4 <- labs_ETR(ETR_plot_21_22_X4))

(Fm_plot_21_22_X4 <- summer_21_22 %>% 
   ggplot(aes(Date, X4.Fm)) +
   geom_line()+  # Add a line that joins the points
   labs(x = "\nDate (day)", y = "Fm \nMoss X4") +
   theme_graphs_env_cond() +
    theme(axis.text.x = element_blank(),
        axis.title.x = element_blank())+  # Remove axis label and text for the graph
    scale_y_continuous(breaks = seq(0, 1300, by = 50))) 

(Fm_plot_21_22_X4 <- labs_fm(Fm_plot_21_22_X4))

(combined_plot_21_22_X4 <- (ETR_plot_21_22_X4/Fm_plot_21_22_X4/Yield_plot_21_22_X4/temp_plot_21_22_X4/PAR_plot_21_22_X4) & plot_layout(ncol = 1))

ggsave(filename = "graphs_appendix/bryum/combined_plot_21_22_X4.png", combined_plot_21_22_X4, width = 16,height = 12, units = "cm", device = "png")  # Save graph

```

4. Summer 2022-2023

Sample X1 (moss)

```{r}
(temp_plot_22_23_X1 <- summer_22_23 %>% 
   ggplot(aes(Date, X1.Temp)) +
   geom_line()+  # Add a line that joins the points
   geom_hline(yintercept = 0, color = "blue", linetype = "dashed") +
   labs(x = "\nDate (day)", y = "Temperature \nMoss X1 (°C)") +
   theme_graphs_env_cond() +
    theme(axis.text.x = element_blank(),
        axis.title.x = element_blank())+  # Remove axis label and text for the graph
   theme_temp())

(temp_plot_22_23_X1 <- labs_temp(temp_plot_22_23_X1))

(PAR_plot_22_23_X1 <- summer_22_23 %>% 
   ggplot(aes(Date, X1.PAR)) +
   geom_line()+  # add a line that joins the points
   labs(x = "\nDate 2022-2023 (day)", y = "PAR \n(µmol m-2 s^-1)") +
   theme_graphs_env_cond()+
   theme_PAR())

(PAR_plot_22_23_X1 <- labs_PAR(PAR_plot_22_23_X1))

(Yield_plot_22_23_X1 <- summer_22_23 %>% 
   ggplot(aes(Date, X1.Y)) +
   geom_line()+  # Add a line that joins the points
   labs(x = "\nDate (day)", y = "Yield \nMoss X1 ") +
   theme_graphs_env_cond() +
   theme(axis.text.x = element_blank(),
        axis.title.x = element_blank())+  # Remove axis label and text for the graph)
   theme_yield())

(Yield_plot_22_23_X1 <- labs_yield(Yield_plot_22_23_X1))

(ETR_plot_22_23_X1 <- summer_22_23 %>% 
   ggplot(aes(Date, X1.ETR)) +
   geom_line()+  # Add a line that joins the points
   labs(x = "\nDate (day)", y = "ETR\n(μmol e- m−2s−1) \nMoss X1") +
   theme_graphs_env_cond() +
   theme(axis.text.x = element_blank(),
        axis.title.x = element_blank()) +  # Remove axis label and text for the graph)
   theme_ETR())

(ETR_plot_22_23_X1 <- labs_ETR(ETR_plot_22_23_X1))

(Fm_plot_22_23_X1 <- summer_22_23 %>% 
   ggplot(aes(Date, X1.Fm)) +
   geom_line()+  # Add a line that joins the points
   labs(x = "\nDate (day)", y = "Fm \nMoss X1") +
   theme_graphs_env_cond() +
   theme(axis.text.x = element_blank(),
        axis.title.x = element_blank())+  # Remove axis label and text for the graph
   scale_y_continuous(breaks = seq(0, 1300, by = 50)) +
   theme_fm())

(Fm_plot_22_23_X1 <- labs_fm(Fm_plot_22_23_X1))

(combined_plot_22_23_X1 <- (ETR_plot_22_23_X1/Fm_plot_22_23_X1/Yield_plot_22_23_X1/temp_plot_22_23_X1/PAR_plot_22_23_X1) & plot_layout(ncol = 1))

ggsave(filename = "graphs_appendix/bryum/combined_plot_22_23_X1.png", combined_plot_22_23_X1, width = 16,height = 12, units = "cm", device = "png")  # Save graph 
```

Sample X2 (moss)

```{r}
(temp_plot_22_23_X2 <- summer_22_23 %>% 
   ggplot(aes(Date, X2.Temp)) +
   geom_line()+  # Add a line that joins the points
   geom_hline(yintercept = 0, color = "blue", linetype = "dashed") +
   labs(x = "\nDate (day)", y = "Temperature \nMoss X2 (°C)") +
   theme_graphs_env_cond() +
    theme(axis.text.x = element_blank(),
        axis.title.x = element_blank())+  # Remove axis label and text for the graph
   theme_temp())

(temp_plot_22_23_X2 <- labs_temp(temp_plot_22_23_X2))

(PAR_plot_22_23_X2 <- summer_22_23 %>% 
    ggplot(aes(Date, X2.PAR)) +
   geom_line()+  # add a line that joins the points
   labs(x = "\nDate 2022-2023 (day)", y = "PAR \n(µmol m-2 s^-1)") +
   theme_graphs_env_cond()+
   theme_PAR())

(PAR_plot_22_23_X2 <- labs_PAR(PAR_plot_22_23_X2))

(Yield_plot_22_23_X2 <- summer_22_23 %>% 
   ggplot(aes(Date, X2.Y)) +
   geom_line()+  # Add a line that joins the points
   labs(x = "\nDate (day)", y = "Yield \nMoss X2 ") +
   theme_graphs_env_cond() +
    theme(axis.text.x = element_blank(),
        axis.title.x = element_blank())+  # Remove axis label and text for the graph)
  theme_yield())

(Yield_plot_22_23_X2 <- labs_yield(Yield_plot_22_23_X2))

(ETR_plot_22_23_X2 <- summer_22_23 %>% 
   ggplot(aes(Date, X2.ETR)) +
   geom_line()+  # Add a line that joins the points
   labs(x = "\nDate (day)", y = "ETR\n(μmol e- m−2s−1) \nMoss X2") +
   theme_graphs_env_cond() +
    theme(axis.text.x = element_blank(),
        axis.title.x = element_blank())+  # Remove axis label and text for the graph)
    theme_ETR())
  
(ETR_plot_22_23_X2 <- labs_ETR(ETR_plot_22_23_X2))

(Fm_plot_22_23_X2 <- summer_22_23 %>% 
   ggplot(aes(Date, X2.Fm)) +
   geom_line()+  # Add a line that joins the points
   labs(x = "\nDate (day)", y = "Fm \nMoss X2") +
   theme_graphs_env_cond() +
    theme(axis.text.x = element_blank(),
        axis.title.x = element_blank())+  # Remove axis label and text for the graph
    scale_y_continuous(breaks = seq(0, 1300, by = 50))+
   theme_fm())
  
(Fm_plot_22_23_X2 <- labs_fm(Fm_plot_22_23_X2))

(combined_plot_22_23_X2 <- (ETR_plot_22_23_X2/Fm_plot_22_23_X2/Yield_plot_22_23_X2/temp_plot_22_23_X2/PAR_plot_22_23_X2) & plot_layout(ncol = 1))

ggsave(filename = "graphs_appendix/bryum/combined_plot_22_23_X2.png", combined_plot_22_23_X2, width = 16,height = 12, units = "cm", device = "png")  # Save graph 
```
Sample X4 (moss)

```{r}
(temp_plot_22_23_X4 <- summer_22_23 %>% 
   ggplot(aes(Date, X4.Temp)) +
   geom_line()+  # Add a line that joins the points
   geom_hline(yintercept = 0, color = "blue", linetype = "dashed") +
   labs(x = "\nDate (day)", y = "Temperature \nMoss X4 (°C)") +
   theme_graphs_env_cond() +
    theme(axis.text.x = element_blank(),
        axis.title.x = element_blank())+ # Remove axis label and text for the graph
   theme_temp())

(temp_plot_22_23_X4 <- labs_temp(temp_plot_22_23_X4))

(PAR_plot_22_23_X4 <- summer_22_23 %>% 
    ggplot(aes(Date, X4.PAR)) +
   geom_line()+  # add a line that joins the points
   labs(x = "\nDate 2022-2023 (day)", y = "PAR \n(µmol m-2 s^-1)") +
   theme_graphs_env_cond()+
  theme_PAR())

(PAR_plot_22_23_X4 <- labs_PAR(PAR_plot_22_23_X4))


(Yield_plot_22_23_X4 <- summer_22_23 %>% 
   ggplot(aes(Date, X4.chosen_yield)) +
   geom_line()+  # Add a line that joins the points
   labs(x = "\nDate (day)", y = "Yield \nMoss X4 ") +
   theme_graphs_env_cond() +
    theme(axis.text.x = element_blank(),
        axis.title.x = element_blank())+  # Remove axis label and text for the graph)
  theme_yield())

(Yield_plot_22_23_X4 <- labs_yield(Yield_plot_22_23_X4))

(ETR_plot_22_23_X4 <- summer_22_23 %>% 
   ggplot(aes(Date, X4.chosen_ETR)) +
   geom_line()+  # Add a line that joins the points
   labs(x = "\nDate (day)", y = "ETR\n(μmol e- m−2s−1) \nMoss X4") +
   theme_graphs_env_cond() +
    theme(axis.text.x = element_blank(),
        axis.title.x = element_blank())+  # Remove axis label and text for the graph)
    theme_ETR())

(ETR_plot_22_23_X4 <- labs_ETR(ETR_plot_22_23_X4))

(Fm_plot_22_23_X4 <- summer_22_23 %>% 
   ggplot(aes(Date, X4.Fm)) +
   geom_line()+  # Add a line that joins the points
   labs(x = "\nDate (day)", y = "Fm \nMoss X4") +
   theme_graphs_env_cond() +
    theme(axis.text.x = element_blank(),
        axis.title.x = element_blank())+  # Remove axis label and text for the graph
    scale_y_continuous(breaks = seq(0, 1300, by = 50)) +
    theme_fm())

(Fm_plot_22_23_X4 <- labs_fm(Fm_plot_22_23_X4))

(combined_plot_22_23_X4 <- (ETR_plot_22_23_X4/Fm_plot_22_23_X4/Yield_plot_22_23_X4/temp_plot_22_23_X4/PAR_plot_22_23_X4) & plot_layout(ncol = 1))

ggsave(filename = "graphs_appendix/bryum/combined_plot_22_23_X4.png", combined_plot_22_23_X4, width = 16,height = 12, units = "cm", device = "png")  # Save graph 
```
