---
title: "DISSERTATION"
format: html
editor: visual
editor_options: 
  chunk_output_type: inline
---

Working directory and load data:

```{r}
setwd("~/Library/CloudStorage/OneDrive-UniversityofEdinburgh/4th year/dissertation/dissertation")
data<-read.csv("Data_PAM_Scott_Base.csv")


```

1.  Load packages

```{r, message=FALSE}
library(skimr)  #summary
library(tidyverse)
library(lubridate)  #dates management
library(gridExtra)  #arrange plots
```

2.  Structure the data

```{r}
skimr::skim(data)
str(data)
tail(data)
head(data)
```

-   only light from mid december to end of february

## Format data that is going to be useful to me

1.  Remove weird times and dates and divide the useful ones

```{r}
data_clean<-data[, -c(2:13)]       #remove columns 2 to 13

data_clean <- data_clean %>% 
  mutate(Date = parse_date_time(Datetime, 'dmy HM'))   #indicate the format the date is wanted

data_clean<-data_clean%>%                             #create new columns with that
  mutate(Month=month(Date))%>%
  mutate(Year=year(Date))%>%
  mutate(Day=day(Date))%>%
  mutate(Hour=hour(Date))%>%
  mutate(Minute=minute(Date))

# Check for rows with parsing issues
problematic_date_rows <- data_clean[is.na(data_clean$Date), ]

# Print the problematic rows
print(problematic_date_rows)
```

Change problematic row 584--\> change value to the correct one and run again

```{r}
data_clean[584, 1]<-"10/02/2019 10:08"

data_clean<-data_clean%>%                             #create new columns with that
  mutate(Month=month(Date))%>%
  mutate(Year=year(Date))%>%
  mutate(Day=day(Date))%>%
  mutate(Hour=hour(Date))%>%
  mutate(Minute=minute(Date))


```

Check new data:

```{r, echo= TRUE, results='hide'}
str(data_clean)
skimr::skim(data_clean)
```

Need to change PAR to numeric, and day, month and year to categories

```{r, echo= TRUE, results='hide'}
data_clean<-data_clean%>%
  mutate(X1.PAR=as.numeric(X1.PAR), X2.PAR=as.numeric(X2.PAR), X3.PAR=as.numeric(X3.PAR), X4.PAR=as.numeric(X4.PAR))%>%
  mutate(Month=as.factor(Month), Year=as.factor(Year), Day= as.factor(Day))


#check
str(data_clean)
```

Data of sensors 1,2 and 4 are for the moss and 3 is for the lichen

### Divide data per year

```{r}
data_2019 <- data_clean %>%
  filter(Year == 2019)

data_2020 <- data_clean %>%
  filter(Year == 2020)

data_2021 <- data_clean %>%
  filter(Year == 2021)

data_2022 <- data_clean %>%
  filter(Year == 2022)
```

# Work with 2019 to see patterns

## Plot the yield and ETR

Yield with months:

```{r}
data_2019%>%
  ggplot(aes(Month,X3.Y..II.))+
  geom_bar(stat = "identity", fill = "grey") +
  labs(x = "Month", y = "Yield")+
  theme_classic()
```

**Only activity in november and december: we are going to plot the last three months**

-   Add the data with the cummulative dates to be able to plot it vs day

```{r}
#filter the values corresponding to the last 3 months

data_clean<- data_clean%>%          #add cummulative dates to data_clean
  mutate(Day.cum=as.factor(data$Date))

data_19_act <- data_clean %>%   # create a data set that only includes info from 2019 Oct, Nov and Dec
  filter(Year == 2019,
         Month %in% c(10, 11, 12))
  

```

Plot the yield data vs by day for the lichen

```{r}

# barplot
data_19_act%>%
  ggplot(aes(Day.cum,X3.Y..II.))+
  geom_bar(stat = "identity", fill = "grey") +
  labs(x = "Day", y = "Yield")+
  theme_classic()+
  theme(axis.text.x = element_text(angle = 90))         #set the x-axis text to be rotated by 90 degrees (vertical) and adjust its horizontal alignment using hjust = 1 to align it to the right. 

#plot with line
data_19_act%>%
  ggplot(aes(Day.cum,X3.Y..II.))+
  geom_point()+
  geom_line()+
  labs(x = "Day", y = "Yield")+
  theme_classic()+
  theme(axis.text.x = element_text(angle = 90)) 
```

**Plot the yield vs day for lichens and mosses**

1.  Calculate average yield value for the moss

```{r}
data_19_act$av.moss.yield<-rowMeans(data_19_act[, c("X1.Y..II.", "X2.Y..II.", "X4.Y..II.")])
```

2.  plot

```{r}

#one option without legend
(p<-data_19_act %>%
  ggplot() +                                                               #don't put aesthetics here
  geom_point(aes(x = Day.cum, y = X3.Y..II.), color = "blue") +           #put asthetics for each different value
  geom_line(aes(x = Day.cum, y = X3.Y..II.), color = "blue") +
  geom_point(aes(x = Day.cum, y = av.moss.yield), color = "red") +
  geom_line(aes(x = Day.cum, y = av.moss.yield), color = "red") +
  labs(x = "Day", y = "Yield") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 90)))

#___________________________________________________________________________#

# Create a data frame for the legend
legend_df <- data.frame(
  Group = c("Lichen", "Moss"),
  Color = c("blue", "darkgreen"))

# Create a scatter plot
(ggplot(data_19_act, aes(x = Day.cum)) +
  geom_point(aes(y = X3.Y..II., color = "Lichen"), data = data_19_act) +
  geom_line(aes(y = X3.Y..II., color = "Lichen"), data = data_19_act) +
  geom_point(aes(y = av.moss.yield, color = "Moss"), data = data_19_act) +
  geom_line(aes(y = av.moss.yield, color = "Moss"), data = data_19_act) +
  labs(x = "Day", y = "Yield") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 90)) +
  scale_color_manual(
    values = legend_df$Color,
    labels = legend_df$Group))



```

\*\*Put the text as day and month

```{r}
data_19_act <- data_19_act %>%
  mutate(Cum_Date_Combined = paste(Month, Day, sep = "-"))%>%   # create a column combining day and month
  mutate(Cum_Date_Combined=as.factor(Cum_Date_Combined))



data_19_act<- data_19_act %>%                                   #put the months as names
  mutate(Month_Name = as.factor(case_when(
    Month == 10 ~ "Oct",
    Month == 11 ~ "Nov",
    Month == 12 ~ "Dec",
    TRUE ~ as.character(Month)  # Keep other months as factors
  )))

str(data_19_act)                                               #check structure

# create a column combining day and month name
data_19_act <- data_19_act %>%
  mutate(Cum_Date_Combined = paste(Day, Month_Name, sep = "-"))%>%   
  mutate(Cum_Date_Combine=as.factor(Cum_Date_Combined))


# Create a data frame for the legend
legend_df <- data.frame(
  Group = c("Lichen", "Moss"),
  Color = c("#ff914d", "#119683"))



# Create a scatter plot
  
ggplot(data_19_act, aes(x = Day.cum)) +
  geom_point(aes(y = X3.Y..II., color = "Lichen"), data = data_19_act) +
  geom_line(aes(y = X3.Y..II., color = "Lichen"), data = data_19_act) +
  geom_point(aes(y = av.moss.yield, color = "Moss"), data = data_19_act) +
  geom_line(aes(y = av.moss.yield, color = "Moss"), data = data_19_act) +
  labs(x = "Day", y = "Photosynthetic Yield") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 90)) +
  scale_color_manual(
    values = legend_df$Color,
    labels = legend_df$Group)+
   scale_x_discrete(
    breaks = data_19_act$Day.cum,  # Specify the numeric values on the axis
    labels = data_19_act$Cum_Date_Combined  # Specify the custom text labels
  )+
  theme(axis.text = element_text(size = 12),  # Adjust the size as needed
          axis.title = element_text(size = 18))


```

Create a graph from mid November, to see everything closer

```{r}
#reduce days

str(data_19_act)
data_19_act$Day.cum<-as.numeric(data_19_act$Day.cum) #put  Day as number and not factor 

d1<-data_19_act%>%
  filter(Day.cum >313)




ggplot(d1,aes(x = Day.cum)) +
  geom_point(aes(y = X3.Y..II., color = "Lichen"), data = d1) +
  geom_line(aes(y = X3.Y..II., color = "Lichen"), data = d1) +
  geom_point(aes(y = av.moss.yield, color = "Moss"), data = d1) +
  geom_line(aes(y = av.moss.yield, color = "Moss"), data = d1) +
  labs(x = "Day", y = "Photosynthetic Yield") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 90)) +
  scale_color_manual(
    values = legend_df$Color,
    labels = legend_df$Group)+
  labs(color=NULL)+ #remove legend title
   scale_x_continuous(      #now change to continous, because Day.cum is numeric
    breaks = d1$Day.cumm,  # Specify the numeric values on the axis
    labels = d1$Cum_Date_Combined  # Specify the custom text labels
  )+
  theme(axis.text = element_text(size = 11),  # Adjust the size as needed
          axis.title = element_text(size = 18),
        legend.text = element_text(size=14)) 

```

**Plot Yield vs PAR for lichens and mosses**

1.  Calculate average PAR value for the moss

```{r}
data_19_act$av.moss.PAR<-rowMeans(data_19_act[, c("X1.PAR", "X2.PAR", "X4.PAR")])
```

2.  Plot

```{r}
legend_df <- data.frame(
  Group = c("Lichen", "Moss"),
  Color = c("blue", "red"))



# Create a scatter plot
ggplot() +
  geom_point(aes(x= X3.PAR, y = X3.Y..II., color = "Lichen"), data = data_19_act) +
  geom_line(aes(x= X3.PAR, y = X3.Y..II., color = "Lichen"), data = data_19_act) +
  geom_point(aes(x=av.moss.PAR, y = av.moss.yield, color = "Moss"), data = data_19_act) +
  geom_line(aes(x=av.moss.PAR, y = av.moss.yield, color = "Moss"), data = data_19_act) +
  labs(x = "PAR (µmol m-2 s-1)", y = "Yield") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 0)) +
  scale_color_manual(
    values = legend_df$Color,
    labels = legend_df$Group)
```

**Plot yield and PAR vs date**

```{r}
legend_df <- data.frame(
  Group = c("Lichen", "Moss"),
  Color = c("blue", "red"))



# Create plot for Yield
plot1<-ggplot(data_19_act, aes(x = Day.cum)) +
  geom_point(aes(y = X3.Y..II., color = "Lichen"), data = data_19_act) +
  geom_line(aes(y = X3.Y..II., color = "Lichen"), data = data_19_act) +
  geom_point(aes(y = av.moss.yield, color = "Moss"), data = data_19_act) +
  geom_line(aes(y = av.moss.yield, color = "Moss"), data = data_19_act) +
  labs(x = "", y = "Yield") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 90)) +
  scale_color_manual(
    values = legend_df$Color,
    labels = legend_df$Group)+
   scale_x_discrete(
    breaks = data_19_act$Day.cumm,  # Specify the numeric values on the axis
    labels = data_19_act$Cum_Date_Combined # Specify the custom text labels
  )

#create plot fior PAR
plot2<-ggplot(data_19_act, aes(Day.cum))+
  geom_point(aes(y = X3.PAR, color = "Lichen"), data = data_19_act) +
  geom_line(aes(y = X3.PAR, color = "Lichen"), data = data_19_act) +
  geom_point(aes(y = av.moss.PAR, color = "Moss"), data = data_19_act) +
  geom_line(aes(y = av.moss.PAR, color = "Moss"), data = data_19_act) +
  labs(y = "PAR (µmol m-2 s-1)", x="Day") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 90)) +
  scale_color_manual(
    values = legend_df$Color,
    labels = legend_df$Group)+
  scale_x_discrete(
    breaks = data_19_act$Day.cumm,  # Specify the numeric values on the axis
    labels = data_19_act$Cum_Date_Combined  # Specify the custom text labels
  )

#combine 2 plots in 1
combined_plot <- grid.arrange(plot1, plot2, ncol = 1) 
```

-   Check lichen PAR→ X3 PAR

    ```{r}
    skimr::skim(data_19_act$X3.PAR)  # it is a character 
    skimr::skim(data_19_act$av.moss.PAR)
    ```

-   put X3.PAR as numeric and run again

```{r}
data_19_act <- data_19_act %>% 
  mutate(X3.PAR = as.numeric(X3.PAR))  # put as numeric


```

2.  Plot

    ```{r}
    legend_df <- data.frame(
      Group = c("Lichen", "Moss"),
      Color = c("blue", "red"))



    # Create a scatter plot
    ggplot() +
      geom_point(aes(x= X3.PAR, y = X3.Y..II., color = "Lichen"), data = data_19_act) +
      geom_line(aes(x= X3.PAR, y = X3.Y..II., color = "Lichen"), data = data_19_act) +
      geom_point(aes(x=av.moss.PAR, y = av.moss.yield, color = "Moss"), data = data_19_act) +
      geom_line(aes(x=av.moss.PAR, y = av.moss.yield, color = "Moss"), data = data_19_act) +
      labs(x = "PAR (µmol m-2 s-1)", y = "Yield") +
      theme_classic() +
      theme(axis.text.x = element_text(angle = 0)) +
      scale_color_manual(
        values = legend_df$Color,
        labels = legend_df$Group)
    ```

**Plot yield and PAR vs date**

```{r}
legend_df <- data.frame(
  Group = c("Lichen", "Moss"),
  Color = c("blue", "red"))



# Create plot for Yield
(plot1<-ggplot(data_19_act, aes(x = Day.cum)) +
  geom_point(aes(y = X3.Y..II., color = "Lichen"), data = data_19_act) +
  geom_line(aes(y = X3.Y..II., color = "Lichen"), data = data_19_act) +
  geom_point(aes(y = av.moss.yield, color = "Moss"), data = data_19_act) +
  geom_line(aes(y = av.moss.yield, color = "Moss"), data = data_19_act) +
  labs(x = "", y = "Yield") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 90)) +
  scale_color_manual(
    values = legend_df$Color,
    labels = legend_df$Group)+
   scale_x_discrete(
    breaks = unique(data_19_act$Day.cum),  # Specify the numeric values on the axis
    labels = unique(data_19_act$Cum_Date_Combined)  # Specify the custom text labels
  )+
    theme(axis.text = element_text(size = 11),  # Adjust the size as needed
          axis.title = element_text(size = 18),
        legend.text = element_text(size=14)))
#create plot fior PAR
(plot2<-ggplot(data_19_act, aes(x = Day.cum))+
  geom_point(aes(y = X3.PAR, color = "Lichen"), data = data_19_act) +
  geom_line(aes(y = X3.PAR, color = "Lichen"), data = data_19_act) +
  geom_point(aes(y = av.moss.PAR, color = "Moss"), data = data_19_act) +
  geom_line(aes(y = av.moss.PAR, color = "Moss"), data = data_19_act) +
  labs(y = "PAR (µmol m-2 s-1)", x="Day") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 90)) +
  scale_color_manual(
    values = legend_df$Color,
    labels = legend_df$Group)+
  scale_x_discrete(
    breaks = unique(data_19_act$Day.cum),  # Specify the numeric values on the axis
    labels = unique(data_19_act$Cum_Date_Combined)  # Specify the custom text labels
  ) +
  theme(axis.text = element_text(size = 11),  # Adjust the size as needed
          axis.title = element_text(size = 18),
        legend.text = element_text(size=14)))

#combine 2 plots in 1
combined_plot <- grid.arrange(plot1, plot2, ncol = 1) 
```

# Notes

14/03/2023

19:06:23

WinControl (rev 1134) report file
